First Measurements of the D(e,e'p)n Cross Section at \\ Very High Recoil Momenta and Large Q^{2}

### 2019-12-17 MY_PUBLICATIONS/PRL/draft_v2/body.tex
update

@@

\includegraphics[scale=0.50]{../prl_plots/PRL_plot1.pdf}

@@

\noindent averaged for overlapping bins in $p_{r}$. The reduced cross sections are defined as follows:

@@

up to $p_{r}\sim750$ MeV/c. At higher missing momentum, however, all models are unable to describe the data, which is currently not well understood.
Given that this is a commissioning experiment that ran

\indent However, given that this experiment ran for only 6 out of the 42 days (21 PAC days assuming 100$\%$ beam efficiency) of beam time and 3 out of the 8 kinematic settings approved in
the original proposal\cite{e12_10_003_proposal}, additional beam time would be required to measure the full kinematic coverage (more missing momentum settings) to gain the necessary statistics 
in order to make any definitive arguments about the underlying physics observed. \\

\indent We acknowledge the outstanding support of the staff of the Accelerator and Physics Divisions at Jefferson Lab
as well as the entire Hall C staff, technicians, graduate students and users who took shifts or contributed
to the equipment for the Hall C upgrade making all four commissioning experiments possible.

>>>>

averaged for overlapping bins in $p_{r}$. 

@@

\includegraphics[scale=0.46]{../prl_plots/PRL_plot1.pdf}

@@

\noindent The reduced cross sections are defined as follows:

@@

up to $p_{r}\sim750$ MeV/c. At higher missing momentum, however, all models are unable to describe the data, which is currently not well understood.\\
\indent Given that this was a commissioning experiment that ran for only 6 out of the 42 days (14.2$\%$) of beam time and 3 out of the 8 original kinematic settings,
additional beam time would be required to measure the full kinematic coverage (more missing momentum settings) to gain the necessary statistics 
in order to make any definitive arguments about the underlying physics observed. \\
\indent We acknowledge the outstanding support of the staff of the Accelerator and Physics Divisions at Jefferson Lab
as well as the entire Hall C staff, technicians, graduate students and users who took shifts or contributed
to the equipment for the Hall C upgrade making all four commissioning experiments possible.
